Energy simulation and analysis of accessory dwelling unit: an evolutionary approach

### 2021-05-28 writing/essay_latex/draft3.tex
draft3 complete

\subsection{Energy simulation and analysis}
Honeybee, part of the open-source Ladybug Tools plugin suite for Grasshopper and Rhino, has become an industry standard for daylighting simulation and energy modeling within architecture and engineering. 
%TODO expand how Honeybee works with energyplus and other tools to calculate energy statistics.
Trees are represented via spherical meshes created using Grasshopper, a visual programming tool for Rhinoceros, and placed where necessary based on the .DWG file. These trees vary in opaque triangulated mesh coverage to simulate foliage cover and to more accurately cast shadows. Originally, trees were represented as simple cylindrical solids, which increased optimization rate and speed of energy analysis, but decreased validity and accuracy of results.

>>>>

\subsection{Energy model and analysis}
Honeybee, part of the open-source Ladybug Tools plugin suite for Grasshopper and Rhino, has become an industry standard for daylighting simulation and energy modeling within architecture and engineering. 
%TODO expand how Honeybee works with energyplus and other tools to calculate energy statistics.
Trees are represented via spherical meshes created using Grasshopper, a visual programming tool for Rhinoceros, and placed where necessary based on the .DWG file. These trees vary in opaque triangulated mesh coverage to simulate foliage cover and to more accurately cast shadows. Originally, trees were represented as simple cylindrical solids, which increased optimization rate and speed of energy analysis, but decreased validity and accuracy of results.
